---
title: "cfToolsData package"
output:
  rmarkdown::html_document
vignette: |
  %\VignetteIndexEntry{cfToolsData package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The *cfToolsData* package provides two pre-trained deep neural network (DNN) 
models for the *cfSort* function.

```{r}
library(cfToolsData)
models <- c(DNN1(), DNN2())
names(models) <- c("DNN1", "DNN2")
models
```

It also provides the shape parameters of beta distribution characterizing 
methylation markers associated with four cancer types for the *CancerDetector* 
function.

```{r}
tumorMarkerParams <- c(
  COAD.tumorMarkerParams.hg19(),
  LIHC.tumorMarkerParams.hg19(),
  LUNG.tumorMarkerParams.hg19(),
  STAD.tumorMarkerParams.hg19()
)
names(tumorMarkerParams) <- c(
    "COAD.tumorMarkerParams",
    "LIHC.tumorMarkerParams",
    "LUNG.tumorMarkerParams",
    "STAD.tumorMarkerParams"
)
tumorMarkerParams
```

Additionally, it includes the shape parameters of beta distribution 
characterizing methylation markers specific to 29 primary human tissue types 
for the *cfDeconvolve* function.

```{r}
tissueMarkerParams <- tissueMarkerParams.hg19()
tissueMarkerParams

tissueMarkerAnnot <- tissueMarkerParams.annot()
tissueMarkerAnnot
```

# Session information

```{r}
sessionInfo()
```
